Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-03-12 paper/abstraction/paper.tex
tweaks for length

\authorinfo{Ryan Beckett}{Princeton University}{rbeckett@cs.princeton.edu}
\authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
\authorinfo{Todd Millstein}{University of California, Los Angeles}{todd@cs.ucla.edu}
\authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
\authorinfo{David Walker}{Princeton University}{dpw@cs.princeton.edu}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/templates}
  \caption{Idealized small configuration component for the data center spine role based on router templates from a large cloud provider (\IE, macros over gobbledygook).}
  \label{fig:templates}
  \vspace{-.8em}
\end{figure}

@@

@@

  \caption{Abstract BGP syntax (left), and compilation from product graphs (right).}
  \label{fig:concretization}
\end{figure*}%

>>>>

\authorinfo{Ryan Beckett}{Princeton University}{rbeckett@cs.princeton.edu}
\authorinfo{Ratul Mahajan}{Microsoft Research}{ratul@microsoft.com}
\authorinfo{Todd Millstein}{UCLA}{todd@cs.ucla.edu}
\authorinfo{Jitendra Padhye}{Microsoft Research}{jpadhye@microsoft.com} 
\authorinfo{David Walker}{Princeton University}{dpw@cs.princeton.edu}

@@

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\columnwidth]{figures/templates}
  \caption{Idealized small configuration component for the data center spine based on templates from a cloud provider.}
  \label{fig:templates}
  \vspace{-1em}
\end{figure}

@@

  \caption{mBGP syntax (left), and compilation from product graphs (right).}
  \label{fig:concretization}
  \vspace{-.8em}
\end{figure*}%
